### 2017-01-03 paper/evaluation.tex
pass on rq2 and added macro CodeIn

To evaluate the presence of parallelization settings, we considered
the \Fix{91} subjects from the groups \emph{long} and \emph{medium}
identified in Section~\ref{sec:rqone}. We focused in these two groups
because they represent costly test suites and are more likely that the
developers may have used strategies to reduce the execution cost (\eg,
running parts of the tests in different threads). We computed the
frequence of the parallelism modes (see Section \ref{sec:modes}) using
a partially manual approach: we first discover automatically the
relevant configuration files and then we manually inspect to eliminate
false-positves (\eg, commented configuration).

>>>>

To evaluate the presence of parallelization settings, we considered
the \Fix{91} subjects from the groups \emph{long} and \emph{medium}
identified in Section~\ref{sec:rqone}. We focused in these two groups
because they represent costly test suites and are more likely that the
developers may have used strategies to reduce the execution cost (\eg,
running parts of the tests in different threads). We computed the
frequence of the parallelism modes (see Section \ref{sec:modes}) using
a semi-automatic approach: we first discover automatically the
relevant configuration files and then we manually inspect them to
eliminate false-positves (\eg, commented configuration).  Figure
\Fix{N} describes the discovery step. We first list the paths of all
build file and then we filter only the build files that contain any of
the keywords, \CodeIn{forkMode}, \CodeIn{forkCount}, or
\CodeIn{parallel}.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
for subj in ${SUBJECTS}; do
    subject_path=${SUBJECTS_HOME}/${subj}
    build_files=`find $subject_path -name pom.xml`
done
\end{lstlisting}
\caption{\label{fig:discovery-step} Bash script \Fix{to do
         something...}. Unnecessary commands are omitted for simplicity.}
\end{figure}
